---
title: "A minimal flipbook"
subtitle: "With flipbookr and xaringan"
author: "You!"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r, include = F}
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F)
library(flipbookr)
library(tidyverse)
```










count: false
 

.panel1-the_chunk-auto[

```{r, eval = F}
cars #<<
```
]
 
.panel2-the_chunk-auto[

```{r, echo = F}
cars
```

]

---
count: false
 

.panel1-the_chunk-auto[

```{r, eval = F}
cars |>
  ggplot() #<<
```

]
 
.panel2-the_chunk-auto[

```{r, echo = F}
cars |>
  ggplot() #<<
```

]



---
count: false
 

.panel1-the_chunk-auto[

```{r, eval = F}
cars |>
   ggplot() +
   aes(x = speed) #<<
```

]
 
.panel2-the_chunk-auto[

```{r, echo = F}
cars |>
   ggplot() +
   aes(x = speed) #<<
```

]

<style>
.panel1-the_chunk-auto {
  color: black;
  width: 38.6060606060606%;
  hight: 32%;
  float: left;
  padding-left: 1%;
  font-size: 80%
}
.panel2-the_chunk-auto {
  color: black;
  width: 59.3939393939394%;
  hight: 32%;
  float: left;
  padding-left: 1%;
  font-size: 80%
}
.panel3-the_chunk-auto {
  color: black;
  width: NA%;
  hight: 33%;
  float: left;
  padding-left: 1%;
  font-size: 80%
}
</style>

